% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{fontawesome5}
% set margins to 1 inch using pandoc 
\usepackage{geometry}
\geometry{margin=0.25in}

% line spacing
\usepackage{setspace}
\setstretch{1.2}


% remove all padding 
\setlength{\parindent}{0pt}

% use Sans Serif font
\renewcommand{\familydefault}{\sfdefault}
% set font size to 14pt
\renewcommand{\normalsize}{\fontsize{12pt}{12pt}\selectfont}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={blue},
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

\hypertarget{simple-markdown-resume-of-dan-slinky-material-linkedin-simple-github-material-email}{%
\section{\texorpdfstring{\faMarkdown Resume of Dan Slinky
\href{https://linkedin.com/in/danslinky}{\faLinkedin}
\href{https://github.com/danslinky}{\faGithub}
\href{mailto:sysadmin@danslinky.co.uk}{\faEnvelope}}{ Resume of Dan Slinky   }}\label{simple-markdown-resume-of-dan-slinky-material-linkedin-simple-github-material-email}}

You can also view this Resume in other formats using my
\href{https://rtfm.danslinky.co.uk/resumes}{Resume as a Service}.

\hypertarget{fontawesome-solid-terminal-introduction}{%
\subsection{\texorpdfstring{\faTerminal
Introduction}{ Introduction}}\label{fontawesome-solid-terminal-introduction}}

As an experienced engineer specializing in Platform, Site Reliability,
and DevSecOps Engineering, I've contributed significantly to designing,
developing, and maintaining diverse projects. With expertise in
container orchestration, I optimize platform performance while ensuring
robust security and seamless integration of machine learning models and
services. Collaborating effectively with multidisciplinary teams,
including engineers, product managers, and stakeholders, I tackle
technical challenges and enhance organizational processes. My focus is
always on delivering solutions that are not only functional but also
easily maintainable, scalable, and observable. Passionate about
fostering a culture of continuous learning and knowledge sharing, I
drive innovation and promote team growth.

I've had the privilege of witnessing the progression of \faDocker
\textbf{Docker}, \faDharmachakra \textbf{Kubernetes}, and the
\textbf{Cloud Native} landscape. Throughout my career, I've refined my
expertise in \textbf{GitOps}, Identity and \textbf{Single Sign-On (SSO)}
integration, and \textbf{Infrastructure as Code (IaC)}, working across a
diverse range cloud platforms. I embrace innovation and actively explore
cutting-edge \textbf{open-source} technologies and manage my personal
infrastructure using \textbf{xcp-ng} and \textbf{OPNSense}. My
unwavering dedication to excellence and continual learning drives me to
deliver top-notch solutions that consistently surpass organizational
goals.

\hypertarget{material-briefcase-career}{%
\subsection{\texorpdfstring{\faBriefcase
Career}{ Career}}\label{material-briefcase-career}}

\hypertarget{material-office-building-adarga}{%
\subsubsection{\texorpdfstring{\faBuilding
Adarga}{ Adarga}}\label{material-office-building-adarga}}

\hypertarget{platform-engineer}{%
\paragraph{2022-2023 Platform Engineer}\label{platform-engineer}}

As a technical leader in the Platform Engineering and SecOps team, I
oversaw operations for a multi-tenanted AI SaaS platform. Utilizing
\textbf{Terragrunt}, \textbf{Terraform}, \faAws , and other platforms, I
ensure robust security and secrets management to meet rigorous customer
requirements, facilitating efficient and reliable deployments through
\textbf{CI/CD} pipelines like \faGithub \textbf{GitHub Actions},
\textbf{CircleCI}, and \textbf{ArgoCD}. Additionally, I spearhead a
significant AWS cost reduction initiative, advocating for FinOps
practices and optimizing cloud spending reporting using tools such as
\textbf{opencost.io}, kubecost, \textbf{Prometheus}, and SysDig,
fostering service ownership and identifying areas for further
optimization. Collaborating on OpenTracing/Telemetry implementation
enhances application observability and performance, particularly in
environments utilizing \textbf{Kafka} and Benthos for message routing.
Expanding the \textbf{SSO} offering by implementing \textbf{SAML}
Microsoft AD integration, supported by Auth0, ensures a seamless user
experience. I assessed the technical feasibility of Plausible web
analytics for platform usage and provide mentorship on implementing
Tigergraph and Neo4j for feature development. Furthermore, I oversaw
recruitment into the team, conducting interviews, promoting team
planning, before transitioning responsibilities to a permanent
Engineering Manager and recruitment team.

\hypertarget{devops-engineer}{%
\paragraph{2017-2019 DevOps Engineer}\label{devops-engineer}}

As the inaugural DevOps at Adarga, I played a pivotal role in
establishing the foundation of an AI SaaS platform, collaborating
closely with engineering and data science teams while leveraging
\textbf{Kubernetes}. My responsibilities encompassed both \faAws and
\faGoogle Cloud environments, where I employed Ansible and YAML for
deploying self-hosted and Cloud Kubernetes clusters and applications.
Embracing a \textbf{microservices} architecture, I integrated
technologies such as \textbf{Kafka}, Python, Java, Node.js,
\textbf{React} single-page applications (SPAs), and \textbf{OAuth2} via
Auth0, alongside implementing the platform API gateway using Kong/nginx
and exploring service mesh options like \textbf{Istio} and Weave.
Moreover, I managed onboarding processes utilizing Apple MDM, fleet DM,
\textbf{osquery}, and Munki, overseeing app packaging and deployment,
while also deploying and maintaining the Atlassian stack, including
\textbf{Jira}, Confluence, and Bamboo.

\hypertarget{material-office-building-cookpad}{%
\subsubsection{\texorpdfstring{\faBuilding
Cookpad}{ Cookpad}}\label{material-office-building-cookpad}}

\hypertarget{site-reliability-engineer}{%
\paragraph{2021 Site Reliability
Engineer}\label{site-reliability-engineer}}

I moved in to the SRE team, taking on a more Global platform
responsibility working closely with colleagues at Cookpad Japan. I
embraced learning \textbf{Golang} and discovered the power of
\textbf{Jsonnet} in this new role. I collaborated with colleagues in the
SRE team to improve documentation, respond to on call incidents, lead
migrations to Kubernetes, and responded to ad hoc support requests.

\hypertarget{machine-learning-infrastructure-engineer}{%
\paragraph{2020 Machine Learning Infrastructure
Engineer}\label{machine-learning-infrastructure-engineer}}

Starting with the MLOps team on a short-term contract, I initially
concentrated on Kubernetes observability before transitioning to a
permanent role focused on Kubernetes ML application deployment. I
deployed Elastic and Prometheus/Thanos for extended metric storage,
coupled with Grafana/Loki to promote ownership of ML applications during
deployment. Furthermore, I revamped Kubernetes application distribution
and deployment by utilizing Kustomize and Flux CD, while also evaluating
Kubeflow/Argo Pipelines for potential future investment.

\hypertarget{material-office-building-torchbox}{%
\subsubsection{\texorpdfstring{\faBuilding
Torchbox}{ Torchbox}}\label{material-office-building-torchbox}}

\hypertarget{systems-administrator}{%
\paragraph{2015-2016 Systems
Administrator}\label{systems-administrator}}

As part of a digital agency supporting Charity and NGO clients with
platforms like Wagtail and Drupal, I spearheaded the relocation of the
Bristol office, ensuring a seamless transition with deployments of
Fibre, Ubiquiti, and MikroTik to establish a fully operational workspace
by Monday morning. Alongside, I delved into Kubernetes, deploying Sensu
and Riemann, among other technologies, to bolster the agency's
infrastructure. Additionally, I tested my resilience in June 2016,
facing challenges head-on with a stiff upper lip.

\hypertarget{material-office-building-future}{%
\subsubsection{\texorpdfstring{\faBuilding
Future}{ Future}}\label{material-office-building-future}}

\hypertarget{operations-engineer}{%
\paragraph{2013-2015 Operations Engineer}\label{operations-engineer}}

I worked as a key figure in a print and digital publishing company
specializing in consumer hobbies and interests, managing global web
properties utilizing CDN, nginx, PHP, RabbitMQ, and Puppet for
infrastructure as code (IaC), with continuous deployment facilitated by
\texttt{rmq://}. Additionally, I led initiatives for data center and
Xen/XCP infrastructure consolidation and upgrade, collaborating on Sensu
observability implementation. Moreover, I designed and implemented
enhanced storage solutions, incorporating recommended LACP groupings and
integrating an advanced storage array for improved reliability and
performance.

\hypertarget{material-train-eurostar}{%
\subsubsection{\texorpdfstring{\faTrain
Eurostar}{ Eurostar}}\label{material-train-eurostar}}

\hypertarget{drupal-devops-engineer}{%
\paragraph{2011-2013 Drupal DevOps
Engineer}\label{drupal-devops-engineer}}

As a Drupal DevOps Engineer specializing in enterprise digital
transformation initiatives, I led the successful relaunch of
eurostar.com utilizing Drupal and ActiveMQ, collaborating closely with
technical partner SNCF. I implemented CI/CD deployment pipelines using
Jenkins, Puppet, and Capistrano to streamline development processes.
Additionally, I provided technical guidance and oversaw the
implementation of Global Load Balancing solutions using
Stingray/ZXTM/Zeus technology. Furthermore, I conducted training
sessions for offshore teams in Mumbai, India, ensuring knowledge
transfer and fostering collaboration across global teams.

\hypertarget{material-office-building-capgemini}{%
\subsubsection{\texorpdfstring{\faBuilding
Capgemini}{ Capgemini}}\label{material-office-building-capgemini}}

\hypertarget{devops-engineer-1}{%
\paragraph{2011-2013 DevOps Engineer}\label{devops-engineer-1}}

I offered Enterprise DevOps capabilities to esteemed clients including
Royal Mail, Burberry, and Michael Page, overseeing deployments on both
AWS and Rackspace platforms. Notably, I spearheaded the relaunch of
eurostar.com using Drupal, ensuring a seamless transition and optimized
performance for the website.

\hypertarget{material-office-building-sift}{%
\subsubsection{\texorpdfstring{\faBuilding
Sift}{ Sift}}\label{material-office-building-sift}}

\hypertarget{operations-engineer-1}{%
\paragraph{2009-2011 Operations Engineer}\label{operations-engineer-1}}

Supporting Drupal 5/6 and WordPress LAMP+, both on-premise and in cloud
with VMWare/ESXi Cloud and XEN co-location setups.

\hypertarget{material-atom-cern}{%
\subsubsection{\texorpdfstring{\faAtom
CERN}{ CERN}}\label{material-atom-cern}}

\hypertarget{technical-student}{%
\paragraph{2007-2008 Technical Student}\label{technical-student}}

During my tenure at \textbf{IT/FIO/LA} \faLinux , I collaborated on
developing innovative Linux PXE/kickstart installation software under
the guidance of J. Polok. Additionally, I contributed to the AIMS2
project, utilizing \faCode Perl, XML/RPC, and Oracle technologies.
Further details about AIMS2 and its ongoing relevance can be found on
the
\href{https://twiki.cern.ch/twiki/bin/view/LinuxSupport/Aims2}{twiki},
including a final presentation to the IT Department, with some
components still in use as of 2024. Volunteering at the 2008 CERN Open
Doors event, I provided guided tours of the CERN Computing Centre,
enthusiastically sharing insights into CERN's IT infrastructure.
Moreover, I played a role in CERN's efforts to lobby the British
Government to support the Technical Student programme, as documented in
this \href{https://cds.cern.ch/record/1120956?ln=en}{publication}.

\hypertarget{material-school-education}{%
\subsection{\texorpdfstring{\faSchool
Education}{ Education}}\label{material-school-education}}

\begin{itemize}
\tightlist
\item
  2009 BA (Hons) Information Systems Analysis at UWE, Bristol
\item
  2005 BTEC National Diploma IT Practitioner at Cornwall College
\end{itemize}

\hypertarget{material-gamepad-personal-interests}{%
\subsection{\texorpdfstring{\faGamepad Personal
Interests}{ Personal Interests}}\label{material-gamepad-personal-interests}}

\begin{itemize}
\tightlist
\item
  I enjoy \faBicycle and have Alpe d'Huez, Col de Braus and Col du
  Turini on my Strava.
\item
  Blue Peter Badge (Standard Issue), issued circa 1996.
\item
  I enjoy digital art, and learning how to use my \faApple Pencil.
\item
  I have a perclusion for metal springs and steps.
\item
  I enjoy reading Douglas Coupland.
\item
  Browser Wars veteran
\item
  \faLinux and open source advocate.
\end{itemize}

\hypertarget{material-thumb-up-endorsements}{%
\subsection{\texorpdfstring{\faThumbsUp
Endorsements}{ Endorsements}}\label{material-thumb-up-endorsements}}

Read more testimonials and endorsements on
\href{https://linkedin.com/in/danslinky}{\faLinkedin} or
\href{https://github.com/danslinky/danslinky.co.uk/issues/new/choose}{\faGithub}.

\begin{quote}
Dan is one of the best platform engineers I've worked with. He has a
vast knowledge of AWS, Kubernetes, Terraform and similar platform
technologies. I learned a lot while working together. He is capable of
taking a vague requirement and converting it into working
infrastructure. He puts thought into the maintainability, scalability
and observability of his solutions and writes good accompanying
documentation. Dan is also a good mentor helping other in the team and
even outside of his team upskill and learn from him.

-- Robert Marsal, Enterprise Architect at Adarga
\end{quote}

\begin{quote}
Dan is one of the most technical platform engineers I've worked with. I
would watch in awe as he calmly debugged and resolved production
incidents. Day to day he is a thoughtful colleague whose advice I would
trust on the design and implementation of cloud native infrastructure
and the general practice of platform engineering.

-- Mark deVilliers, Engineering Leader
\end{quote}

\end{document}
